### 2019-03-15 papers/journal/intro.tex
added the combi. problem subsection

Previous analyses of vesicle traffic networks dealt with this combinatorial
explosion by using a sampling approach~\cite{mani2016stacking}. 
%
In these analyses, vesicle traffic is
modelled as a dynamical system. 
%
The traffic rule specifies how the system transitions from one
time point to the next. 
%
Given a traffic rule and an initial condition, the system is evolved over
time until a steady state is reached. 
%
By studying a large sample of randomly generated traffic
rules, such analyses can make statistical claims about vesicle traffic. 
%

In contrast, here we seek understand properties of vesicle traffic networks over all possible traffic rules, not just for a sampled subset. 
%
We would also like to directly make statements about steady state properties, rather
than using transition dynamics to first search for steady states. 
%
Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
%
The tools model the computation symbolically for the graphs of finite size and can verify the and hence make prediction about the hypothesis for all possible states of the system. 
%

>>>>

Previous analyses of vesicle traffic networks dealt with this combinatorial
explosion by using a sampling approach~\cite{mani2016stacking}. 
%
In these analyses, vesicle traffic is modelled as an update system. 
%
%The traffic rule specifies how the system transitions from one
%time point to the next. 
%
Given a traffic rule and an initial condition, the system is updates one step a time, updating molecular flux of the compartments, until a steady state is reached. 
%
The update rule defines the flux transition for the next step. 
%
By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
%

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
%
We would also like to directly make statements about steady state properties, rather
than using transition dynamics to first search for steady states. 
%
Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
%
The tools model the computation symbolically for the graphs of finite size and can verify the and hence make prediction about the hypothesis for all possible states of the system. 
%
